\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
%Setup hyperref package, and colours for links
\usepackage{hyperref}
\usepackage{fontspec}
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = SourceSansPro-Bold.otf,
ItalicFont = SourceSansPro-LightIt.otf
]
{SourceSansPro-Light.otf}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\Huge \scshape {Jared Pinargote}}\\
    Lehi, UT $\cdot$ jaredpnrgt@yahoo.com $\cdot$ 301-821-0941 $\cdot$ \href{https://www.linkedin.com/in/jared-pinargote}{https://www.linkedin.com/in/jared-pinargote}
\end{center}

%==== Education ====%
\header{Education}
\textbf{Brigham Young University - Idaho}\hfill Rexburg, ID\\
BS Software Engineering \textit{GPA: 3.8} \hfill Jan 2016 - Dec 2017\\
\vspace{2mm}

\header{Projects}
{\textbf{Interior Planning - Geomni}} {\sl ARKit, iOS Development} \\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
    \item Creates floor plans by users scanning walls in augmented reality (AR).
    \item Corrects for noise and drift using geometric algorithms to align walls and rooms to each other.
    \item Intuitive design allows users to quickly learn and produce plans quicker than current AR floor plan creators with more accurate results.
    \item Experience with mobile development, MVVM architecture, and simulated annealing, a meta-heuristic AI algorithm.
\end{itemize}

{\textbf{Caption Game - School}} {\sl HTML, Node.JS, jQuery, PostgreSQL} \\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
    \item Online game where users come together in a room using a room code
    \item Step-by-step process had users make drawings and captions to later combine to make funny images which were later voted on, determining a winner.
    \item Far exceeded project requirements due to prior personal experience with web development
    \item Experience with Node.JS to handle the back-end, jQuery and Bootstrap to handle the front-end, and PostgreSQL to store images, captions, rooms and users.
\end{itemize}

{\textbf{VR Reddit Client - Personal}} {\sl Unity3D, C\#, Oculus SDK, Oculus Rift} \hfill https://github.com/jaredpinargote/RedditForRift\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
    \item Virtual reality client to access reddit.com. Users can quickly view more content than on a monitor or phone.
    \item A physics-based interface allows for intuitive interactions, similar to sorting through a box of photos.
    \item Experience with asynchronous programming and .NET 4.6
\end{itemize}

{\textbf{VR Music Visualizer - School}} {\sl Unity3D, C\#, Oculus SDK, Gear VR} \\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
    \item Music visualizer for mobile that allows users to navigate their file system in VR, select a song, and view an audio reactive environment with some interaction using a 3-DoF controller.
    \item Experience with C\# and real-time signal analysis.
\end{itemize}

\vspace*{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Geomni} \hfill Lehi, Utah\\
\textit{AR Software Engineer} \hfill December 2017 | Present\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
    \item Develop augmented reality solutions for insurance adjusters
    \item Technical lead in producing geometric algorithms to correct for ARKit limitations
    \item Ensure maintainability of code for optimal teamwork
\end{itemize}
\textbf{EZNetTools} \hfill Rexburg, ID\\
\textit{Software Engineer} \hfill February 2017 | September 2017\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
    \item Develop software for internal company use
    \item Maintain and update client-facing production software
    \item Address company server issues
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
    Programming: & Swift, C\#, C++, Kotlin, JavaScript, jQuery, HTML, Node.JS                                                  \\
    Languages:      & English, Spanish, Portuguese                                             \\
    Interpersonal:         & Cooperative, Team Leader, Written Communication, Public Speaking         \\
    Other:                 & Rapid Prototyping, Linear Algebra, Calculus, Geometry, Kinematic Physics \\
\end{tabular}
\vspace{2mm}

\header{Volunteer}
\textbf{Missionary - The Church of Jesus Christ of Latter-day Saints} \hfill May 2013 - April 2015\\
Spent two years as a church representative planning meetings, setting goals, and organizing mission work. Visited the needy and helped maintain church organization in Espirito Santo, Brazil. Learned to cooperate with people from differing backgrounds and culture.\\
\vspace*{2mm}

\ 
\end{document}